WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-14 ms.tex
Add future work section

All simulated sources have component masses distributed uniformly between 1.2 and 1.6\,$M_\odot$ and randomly oriented spins with dimensionless magnitudes $\chi$ between -0.05 and +0.05. Sky positions and binary orientations are random and isotropic. Distances are drawn uniformly from ${D_\mathrm{L}}^3$, reflecting a uniform source population (neglecting cosmological effects, which are small within the Advanced \acs{LIGO} \ac{BNS} range).

@@

>>>>

All simulated sources have component masses distributed uniformly between 1.2 and 1.6\,$M_\odot$ and randomly oriented spins with dimensionless magnitudes $\chi = c|\mathbf{S}|/Gm^2$ between -0.05 and +0.05. Sky positions and binary orientations are random and isotropic. Distances are drawn uniformly from ${D_\mathrm{L}}^3$, reflecting a uniform source population (neglecting cosmological effects, which are small within the Advanced \acs{LIGO} \ac{BNS} range).

@@

\section{Future work}

One immediately pressing direction for future work is to address the issue of sub\nobreakdashes-threshold signals, as this will be a major issue when Advanced Virgo comes online in 2016\nobreakdashes--2017. Using the full \ac{SNR} time series in place of the autocorrelation function seems like a promising avenue; implementing this requires some infrastructure changes to both the matched filter pipeline and \ac{BAYESTAR}.

A more open question is how to account for spin precession. The simulations in \cite{FirstTwoYears} and in this paper featured extremely modest spins of $\chi \leq 0.05$, consistent with the fastest known pulsars in binaries \citep{2003Natur.426..531B,DetectingBNSSystemsWithSpin}. The signals were detected using a template bank that lacked spins entirely. Farr et al. (in preparation) show that using nonspinning \ac{BNS} templates for parameter estimation has negligible impact on sky localization. However, if one or both companions are spinning as fast as a millisecond pulsar, $\chi \sim 0.4$ \cite{FastestSpinningMillisecondPulsar}, or even near breakup, $\chi \sim 0.7$, then the orbital plane may precess; in this case, spins can no longer be neglected for detection \cite{DetectingBNSSystemsWithSpin} and may also be important for parameter estimation. Since spinning \ac{BNS} searches are still an active area of development, \ac{BAYESTAR}'s sky localization accuracy in this regime should be reexamined in the future.
